---
title: "`r params$report_title`"
subtitle: "KiwiFlow `r params$version`  -  Released `r params$date`"
author: "`r params$report_author`"
date: "`r Sys.Date()`"
params:
  report_title: "Deconvolution Report"
  report_author: ""
  comment: ""
  result_path: ""
  result_file: ""
  version: ""
  date: ""
  temp_dir: ""
output:
  html_document:
    self_contained: true
    embed-resources: true
title-block-banner: "#27445C"
css: quarto_styles.css
format:
  html:
    smooth-scroll: true
    embed-resources: true
    other-links:
      - text: KiwiFlow Repository
        icon: github
        href: https://github.com/infinity-a11y/KiwiFlow
        target: _blank
      - text: UniDec Repository
        icon: github
        href: https://github.com/michaelmarty/UniDec
        target: _blank
      - text: Liora Bioinformatics
        href: https://www.liora-bioinformatics.com/
        target: _blank
---

<button onclick="topFunction()" id="topBtn" class="btn btn-primary">↑ Back to Top</button>

<script>
  // Get the button
  let mybutton = document.getElementById("topBtn");

  // Show the button when scrolling down
  window.onscroll = function () {
    if (document.body.scrollTop > 200 || document.documentElement.scrollTop > 200) {
      mybutton.style.display = "block";
    } else {
      mybutton.style.display = "none";
    }
  };

  // Scroll to the top smoothly
  function topFunction() {
    window.scrollTo({ top: 0, behavior: 'smooth' });
  }
</script>

<style>
  #topBtn {
    position: fixed;
    bottom: 20px;
    right: 20px;
    display: none;
    padding: 10px 15px;
    font-size: 16px;
    border: none;
    border-radius: 5px;
    cursor: pointer;
  }
</style>


```{r }
#| label: List Result
#| message: false
#| warning: false
#| include: false

# Load the result list from RDS file
result <- readRDS(file.path(params$result_file))
names_result <- names(result$deconvolution)[
  !names(result$deconvolution) %in% c("session", "output")
]
```

`r if(params$comment != "") paste("<div class='comment-text'>", params$comment, "</div> <hr>")`

### Parameter

``` {r}
#| label: Load Result
#| message: false
#| warning: false
#| include: false

# Load the result list from RDS file
config_all <- unlist(result$deconvolution[[1]][[1]])
names(config_all) <- gsub("config.", "", names(config_all))

imp_params <- names(config_all) %in%
  c(
    "startz",
    "endz",
    "minmz",
    "maxmz",
    "masslb",
    "massub",
    "peakwindow",
    "peakthresh",
    "peaknorm",
    "massbins"
  )

main_params <- config_all[imp_params]

config_ex_path <- config_all[!names(config_all) %in% c("input", "output")]
```


```{r echo=FALSE, results='asis'}
#| label: Parameter

main_param_table <- data.frame(
  Parameter = names(main_params),
  Value = as.character(main_params),
  stringsAsFactors = FALSE
)

# Split main_param_table into three parts for a 6-column format
third_n_main <- ceiling(nrow(main_param_table) / 3)

main_left <- main_param_table[1:third_n_main, ]
main_middle <- main_param_table[(third_n_main + 1):(2 * third_n_main), ]
main_right <- main_param_table[(2 * third_n_main + 1):nrow(main_param_table), ]

# Pad shorter columns with empty rows
max_rows_main <- max(nrow(main_left), nrow(main_middle), nrow(main_right))

if (nrow(main_left) < max_rows_main) {
  empty_rows <- data.frame(
    Parameter = rep("", max_rows_main - nrow(main_left)),
    Value = rep("", max_rows_main - nrow(main_left))
  )
  main_left <- rbind(main_left, empty_rows)
}

if (nrow(main_middle) < max_rows_main) {
  empty_rows <- data.frame(
    Parameter = rep("", max_rows_main - nrow(main_middle)),
    Value = rep("", max_rows_main - nrow(main_middle))
  )
  main_middle <- rbind(main_middle, empty_rows)
}

if (nrow(main_right) < max_rows_main) {
  empty_rows <- data.frame(
    Parameter = rep("", max_rows_main - nrow(main_right)),
    Value = rep("", max_rows_main - nrow(main_right))
  )
  main_right <- rbind(main_right, empty_rows)
}

# Combine into final 6-column format for main parameters
main_param_table_wide <- cbind(main_left, main_middle, main_right)

param_table <- data.frame(
  Parameter = names(config_ex_path),
  Value = as.character(config_ex_path),
  stringsAsFactors = FALSE
)

# Determine the third of the remaining parameters
third_n <- ceiling(nrow(param_table) / 3)

# Split into three parts for a 6-column format
param_left <- param_table[1:third_n, ]
param_middle <- param_table[(third_n + 1):(2 * third_n), ]
param_right <- param_table[(2 * third_n + 1):nrow(param_table), ]

# Pad the shorter columns with empty rows if necessary
max_rows <- max(nrow(param_left), nrow(param_middle), nrow(param_right))

if (nrow(param_left) < max_rows) {
  empty_rows <- data.frame(
    Parameter = rep("", max_rows - nrow(param_left)),
    Value = rep("", max_rows - nrow(param_left))
  )
  param_left <- rbind(param_left, empty_rows)
}

if (nrow(param_middle) < max_rows) {
  empty_rows <- data.frame(
    Parameter = rep("", max_rows - nrow(param_middle)),
    Value = rep("", max_rows - nrow(param_middle))
  )
  param_middle <- rbind(param_middle, empty_rows)
}

if (nrow(param_right) < max_rows) {
  empty_rows <- data.frame(
    Parameter = rep("", max_rows - nrow(param_right)),
    Value = rep("", max_rows - nrow(param_right))
  )
  param_right <- rbind(param_right, empty_rows)
}

# Combine into final table structure with 6 columns
param_table_wide <- cbind(param_left, param_middle, param_right)

# Remove column names for all tables
colnames(main_param_table_wide) <- NULL
colnames(param_table_wide) <- NULL

# Render main parameter table with no headers
main_param_tab <- knitr::kable(
  main_param_table_wide,
  booktabs = TRUE,
  row.names = FALSE,
  align = "l"
) |>
  kableExtra::kable_styling(
    full_width = TRUE,
    bootstrap_options = c("hover", "condensed")
  ) |>
  kableExtra::column_spec(c(2, 4, 6), monospace = TRUE) |>
  kableExtra::kable_styling("striped")


# Create table with the updated 6 columns
other_param_tab <- knitr::kable(
  param_table_wide,
  booktabs = TRUE,
  row.names = FALSE,
  align = "l"
) |>
  kableExtra::kable_styling(
    full_width = TRUE,
    bootstrap_options = c("hover", "condensed")
  ) |>
  kableExtra::column_spec(c(2, 4, 6), monospace = TRUE) |>
  kableExtra::kable_styling("striped")

# Print tables with a break in between
cat(main_param_tab)
cat("<div style='overflow-x: auto; width: 100%;'>")
cat("</div>")
cat("<br><details>  <summary>Parameter Full List</summary> ")
cat(other_param_tab)
cat("</details>")
```

------------------------------------------------------------------------

### Results

```{r echo=FALSE, results="asis"}
#| label: Heatmap

if (file.exists(file.path(params$temp_dir, "heatmap.rds"))) {
  heatmap <- readRDS(file.path(params$temp_dir, "heatmap.rds"))
  htmltools::tagList(
    htmltools::div(
      style = "max-width: 65%;",
      heatmap
    )
  )
}
```

```{r echo=FALSE, results="asis"}
#| label: Sample List
#| message: false
#| warning: false

if (length(names_result) > 1) {
  # Define the number of columns
  num_cols <- 2

  # Generate clickable list of names in two columns with alternating row colors
  table_rows <- sapply(
    seq(1, length(names_result), by = num_cols),
    function(i) {
      row_color <- ifelse((i %/% num_cols) %% 2 == 0, "#f2f2f27a", "#ffffff") # Alternate row colors

      # Create cells for each column
      cells <- lapply(i:(i + num_cols - 1), function(j) {
        if (j <= length(names_result)) {
          paste0(
            "<td><a href='#",
            tolower(names_result[j]),
            "'>",
            names_result[j],
            "</a></td>"
          )
        } else {
          "<td></td>" # Empty cell for uneven rows
        }
      })

      paste0(
        "<tr style='background-color:",
        row_color,
        ";'>",
        paste(unlist(cells), collapse = ""),
        "</tr>"
      )
    }
  )

  # Convert table rows to a single character string with table structure
  clickable_table <- paste(
    "<table class='table table-bordered' style='width:100%; border-collapse: collapse;'>",
    paste(table_rows, collapse = "\n"),
    "</table>",
    sep = "\n"
  )

  cat("<br>", clickable_table)
}

```

```{r echo=FALSE, fig.height=6, fig.show='hold', fig.width=10, results='asis'}
#| label: Results
#| message: false
#| warning: false

# Function to convert ggplot to Base64
ggplot_to_base64 <- function(plot, width = 5, height = 5, dpi = 300) {
  temp_file <- tempfile(fileext = ".png") # Create temp file

  ggplot2::ggsave(
    temp_file,
    plot = plot,
    width = width,
    height = height,
    dpi = dpi,
    device = "png"
  )

  base64_data <- base64enc::dataURI(file = temp_file, mime = "image/png") # Convert to Base64

  unlink(temp_file) # Delete temp file

  return(base64_data)
}

# Store image sections in a list for rendering
plot_output <- list()

for (name in names_result) {
  if (
    !is.null(result$deconvolution[[name]]$decon_spec) &&
      !is.null(result$deconvolution[[name]]$raw_spec)
  ) {
    # Convert ggplots to Base64 without saving to disk
    img1_base64 <- ggplot_to_base64(result$deconvolution[[name]]$decon_spec)
    img2_base64 <- ggplot_to_base64(result$deconvolution[[name]]$raw_spec)

    config <- result$deconvolution[[name]]$config

    config_path <- ifelse(
      length(config$input) > 1,
      paste(config$input[1], config$input[2]),
      config$input
    )

    # Create a linked section header and horizontal separator
    section_html <- htmltools::tagList(
      htmltools::tags$section(
        id = tolower(name),
        class = "level4",
        htmltools::h4(
          class = "anchored",
          `data-anchor-id` = tolower(name),
          htmltools::span(class = "name-part", paste(name)),
          " ",
          htmltools::span(
            class = "subtitle-part",
            "Deconvoluted Spectrum | Original Raw Spectrum"
          ),
          htmltools::a(
            class = "anchorjs-link",
            `aria-label` = "Anchor",
            `data-anchorjs-icon` = "\uE84B",
            href = paste0("#", tolower(name)),
            style = "font: 1em / 1 anchorjs-icons; margin-left: 0.1875em; padding-right: 0.1875em;"
          )
        ),
        htmltools::div(
          class = "result-path",
          style = "overflow-wrap: anywhere;",
          htmltools::p(normalizePath(dirname(config_path)))
        ),
        # Side-by-side images
        htmltools::div(
          style = "display: flex;",
          htmltools::img(src = img1_base64, width = "50%"),
          htmltools::img(src = img2_base64, width = "50%")
        )
      )
    )

    # Append the section to the output list
    plot_output <- append(plot_output, list(section_html))
  }
}

# Force Quarto to recognize and render everything
htmltools::tagList(plot_output)
```

`r paste("<br><br>Session:<i>", paste0(Sys.Date(), "_", regmatches(     basename(result$session[3]),     regexpr("id\\d+", basename(result$session[3])) )), "</i>")`

------------------------------------------------------------------------